---
title: "icd10 for maggic"
editor_options:
  chunk_output_type: console
output:
  pdf_document: default
  html_document: default
authors: Ayoub Bagheri
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


## Load libraries

```{r}
library(xlsx)
library(dplyr)
library(topicmodels)
library(tidytext)
library(ggplot2)
library(tm)
library(stringr)
library(skimr)
library(magrittr)
library(glmnet)
library(qdap)
library(caret)
library(pROC)
library(wordcloud)
library(mice)
library(ROCR)
library(tidyr)
library(text2vec)
library(readr)
library(e1071)
library(tidyverse)

```

# 0. Exploratory data analysis
## Reading patient letters

```{r}
icd.data <-
  read.xlsx("Data/anonym.xlsx", 1)

```


## Statistics of data
```{r}
names(icd.data)
skim(icd.data)
skim(icd.data$Diagnosecode)
table(icd.data$Diagnosecode)

# number of patients = 5548
length(unique(icd.data$PATIENT_ID_VOORKEUR))

```

NA values
```{r}
# na_index <- is.na(icd.data$Diagnosecode)
# X <- icd.data[!na_index, ]
# skim(X)

```

# Preprocessing 1
## keep only the first part of the icd10
```{r}
icd.data$Diagnosecodeerst <- Trim(icd.data$Diagnosecode)
icd.data$Diagnosecodeerst <- gsub(",", ".", icd.data$Diagnosecodeerst)
icd.data$Diagnosecodeerst <- gsub("\\..*", "", icd.data$Diagnosecodeerst)
icd.data$Diagnosecodeerst <- substr(icd.data$Diagnosecodeerst, 1, 3)
table(icd.data$Diagnosecodeerst)
skim(icd.data$Diagnosecodeerst)

a <- ggplot(icd.data, aes(Diagnosecodeerst))

a +  geom_bar(fill = "#0073C2FF") +
  theme_minimal()

ggplot(icd.data, aes(Diagnosecodeerst)) + geom_density()

icd.data$Diagnosechapter <- 0

for(row in 1:nrow(icd.data)){
   if(icd.data[row,]$Diagnosecodeerst >= 'A00' & 
      icd.data[row,]$Diagnosecodeerst <= 'B99')
     icd.data[row,]$Diagnosechapter = 1
   else if(icd.data[row,]$Diagnosecodeerst >= 'C00' & 
      icd.data[row,]$Diagnosecodeerst <= 'D48')
     icd.data[row,]$Diagnosechapter = 2
   else if(icd.data[row,]$Diagnosecodeerst >= 'D50' & 
      icd.data[row,]$Diagnosecodeerst <= 'D89')
     icd.data[row,]$Diagnosechapter = 3
   else if(icd.data[row,]$Diagnosecodeerst >= 'E00' & 
      icd.data[row,]$Diagnosecodeerst <= 'E90')
     icd.data[row,]$Diagnosechapter = 4
   else if(icd.data[row,]$Diagnosecodeerst >= 'F00' & 
      icd.data[row,]$Diagnosecodeerst <= 'F99')
     icd.data[row,]$Diagnosechapter = 5
   else if(icd.data[row,]$Diagnosecodeerst >= 'G00' & 
      icd.data[row,]$Diagnosecodeerst <= 'G99')
     icd.data[row,]$Diagnosechapter = 6
   else if(icd.data[row,]$Diagnosecodeerst >= 'H00' & 
      icd.data[row,]$Diagnosecodeerst <= 'H59')
     icd.data[row,]$Diagnosechapter = 7
   else if(icd.data[row,]$Diagnosecodeerst >= 'H60' & 
      icd.data[row,]$Diagnosecodeerst <= 'H95')
     icd.data[row,]$Diagnosechapter = 8
   else if(icd.data[row,]$Diagnosecodeerst >= 'I00' & 
      icd.data[row,]$Diagnosecodeerst <= 'I99')
     icd.data[row,]$Diagnosechapter = 9
   else if(icd.data[row,]$Diagnosecodeerst >= 'J00' & 
      icd.data[row,]$Diagnosecodeerst <= 'J99')
     icd.data[row,]$Diagnosechapter = 10
   else if(icd.data[row,]$Diagnosecodeerst >= 'K00' & 
      icd.data[row,]$Diagnosecodeerst <= 'K93')
     icd.data[row,]$Diagnosechapter = 11
   else if(icd.data[row,]$Diagnosecodeerst >= 'L00' & 
      icd.data[row,]$Diagnosecodeerst <= 'L99')
     icd.data[row,]$Diagnosechapter = 12
   else if(icd.data[row,]$Diagnosecodeerst >= 'M00' & 
      icd.data[row,]$Diagnosecodeerst <= 'M99')
     icd.data[row,]$Diagnosechapter = 13
   else if(icd.data[row,]$Diagnosecodeerst >= 'N00' & 
      icd.data[row,]$Diagnosecodeerst <= 'N99')
     icd.data[row,]$Diagnosechapter = 14
   else if(icd.data[row,]$Diagnosecodeerst >= 'O00' & 
      icd.data[row,]$Diagnosecodeerst <= 'O99')
     icd.data[row,]$Diagnosechapter = 15
   else if(icd.data[row,]$Diagnosecodeerst >= 'P00' & 
      icd.data[row,]$Diagnosecodeerst <= 'P96')
     icd.data[row,]$Diagnosechapter = 16
   else if(icd.data[row,]$Diagnosecodeerst >= 'Q00' & 
      icd.data[row,]$Diagnosecodeerst <= 'Q99')
     icd.data[row,]$Diagnosechapter = 17
   else if(icd.data[row,]$Diagnosecodeerst >= 'R00' & 
      icd.data[row,]$Diagnosecodeerst <= 'R99')
     icd.data[row,]$Diagnosechapter = 18
   else if(icd.data[row,]$Diagnosecodeerst >= 'S00' & 
      icd.data[row,]$Diagnosecodeerst <= 'T98')
     icd.data[row,]$Diagnosechapter = 19
   else if(icd.data[row,]$Diagnosecodeerst >= 'V01' & 
      icd.data[row,]$Diagnosecodeerst <= 'Y98')
     icd.data[row,]$Diagnosechapter = 20
   else if(icd.data[row,]$Diagnosecodeerst >= 'Z00' & 
      icd.data[row,]$Diagnosecodeerst <= 'Z99')
     icd.data[row,]$Diagnosechapter = 21
   else
     icd.data[row,]$Diagnosechapter = 22
}

table(icd.data$Diagnosechapter)
skim(icd.data$Diagnosechapter)

# b <- ggplot(icd.data, aes(Diagnosechapter))
# 
# b + geom_bar(fill = "black") +
#   theme_minimal()

df_code <- icd.data %>%
  group_by(Diagnosecode) %>%
  summarise(counts = n())

df_3digit <- icd.data %>%
  group_by(Diagnosecodeerst) %>%
  summarise(counts = n())

df <- icd.data %>%
  group_by(Diagnosechapter) %>%
  summarise(counts = n())

df <- df[order(df$counts),]
# ggplot(df, aes(x = Diagnosechapter, y = counts)) +
#   geom_point() + geom_abline() + theme_minimal()

ggplot(df, aes(x = Diagnosechapter, y = counts)) +
  geom_bar(stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) + 
  scale_x_continuous("Chapter", 
                     labels = as.character(df$Diagnosechapter), 
                     breaks = df$Diagnosechapter) +
  theme_minimal()

ggplot(df_3digit, aes(x = Diagnosecodeerst, y = counts)) +
  geom_point() +
  xlab("3digit") +
  theme_minimal()

# 3-digit plots
df_3digit$group <- as.numeric(cut(df_3digit$counts, 2))
ggplot(df_3digit, aes(x = factor(Diagnosecodeerst), y = counts)) + 
  geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  xlab("3digit") +
  facet_wrap(~group, ncol = 1, scales = "free_x")


df_3digit_sub <- subset(df_3digit, counts > 399)

ggplot(df_3digit_sub, aes(x = Diagnosecodeerst, y = counts)) +
   geom_bar(stat = "identity") +
  geom_text(aes(label = counts), vjust = -0.3) +
  xlab("3digit_sub") +
  theme_minimal()

sorted3 <- df_3digit_sub %>% arrange(rev(Diagnosecodeerst))

sorted3$text_labels <- c("Presence of cardiac and vascular implants and grafts", "Personal history of certain other diseases", "Personal history of malignant neoplasm", "Pain in throat and chest", "Chronic kidney disease", "Other chronic obstructive pulmonary disease", "Heart failure", "Other cardiac arrhythmias", "Atrial fibrillation and flutter", "Paroxysmal tachycardia", "Atrioventricular and left bundle-branch block", "Cardiomyopathy", "Nonrheumatic aortic valve disorders", "Chronic ischaemic heart disease", "Acute myocardial infarction", "Essential (primary) hypertension", "Disorders of lipoprotein metabolism and other lipidaemias", "Type 2 diabetes mellitus")
  
ymid <- mean(range(df_3digit_sub$counts))

sorted3 %>% 
  arrange(counts) %>% 
  mutate(letter = str_extract(Diagnosecodeerst, "\\w"),
         Diagnosecodeerst = as_factor(Diagnosecodeerst)) %>% 
  ggplot(aes(x = Diagnosecodeerst, y = counts, fill = letter)) + 
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks=seq(0, 3000, 200)) +
  geom_text(mapping = aes(label = text_labels, hjust = ifelse(counts < ymid, -0.1, 1.1)), 
            size = 4) +
  labs(x = "Diagnosis code", fill = "Category") +
  # theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  coord_flip() +
  theme_minimal() +
  
  scale_fill_grey(start = 0.5, end = 0.9)


# code plots
df_code$group <- as.numeric(cut(df_code$counts, 21))
ggplot(df_code, aes(x = factor(Diagnosecode), y = counts)) + 
  geom_bar(stat = "identity") + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  xlab("Code") + 
  scale_y_continuous(breaks=seq(0, 3000, 200)) +
  facet_wrap(~group, ncol = 4, scales = "free_x")

df_code_sub0 <- subset(df_code, counts < 100)
df__code_sub0_an <- df_code_sub0 %>%
  group_by(counts) %>%
  summarise(RAREcounts = n())

ggplot(df__code_sub0_an, aes(x = factor(counts), y = RAREcounts)) + 
  geom_bar(stat = "identity") + 
  xlab("Appearance") +
  ylab("Number of rare ICD-10 code") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5)) +
  geom_text(aes(label = RAREcounts), vjust = -0.3)
  

df_code_sub <- subset(df_code, counts > 99)

ggplot(df_code_sub, aes(x = Diagnosecode, y = counts)) + 
  geom_bar(stat = "identity") +
  scale_y_continuous(breaks=seq(0, 3000, 200)) +
  # geom_text(aes(label = counts), vjust = -0.3) +
  xlab("Diagnosis code") +
  # theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  coord_flip() +
  theme_minimal()


# # df <- df %>%
# #   mutate(prop = round(counts*100/sum(counts), 1))
# #          # lab.ypos = cumsum(prop) - 0.5*prop)
# head(df, 4)

```


## Text preprocessing: cleaning function
```{r}
setwd("Data/")
clean_text  <- function(text){
  text      <- tolower(text)
  text      <- gsub("[[:punct:][:blank:]]+", " ", text)
  text      <- stripWhitespace(text)
  text      <- removeNumbers(text)
  text      <- removePunctuation(text)
  # create a customized stop list by editting the stop.txt file
  new_stops <- read.table("stop.txt", header = TRUE)
  new_stops <- as.vector(new_stops$CUSTOM_STOP_WORDS)
  text      <- removeWords(text, new_stops)
  return(text)
  }

```

## clean text
```{r}
icd.data$deidentified <- clean_text(icd.data$deidentified)

```

## separate subparts
```{r}
icd.data$samenvatting <- substring(icd.data$deidentified, 
                           regexpr("samenvatting", icd.data$deidentified) + 13)

```

## removing long words and words between <>
```{r}
icd.data$deidentified <- gsub("\\b[[:alnum:]]{15,}\\b", "", 
                              icd.data$deidentified, perl = T)
icd.data$deidentified <- gsub("\\s*\\<[^\\>]+\\>", "", 
                              icd.data$deidentified, perl = T)


```

## min, max, avg van samenvatting
```{r}
n    <- 0
minl <- 10000
maxl <- 0
sl   <- 0
for (i in 1:dim(icd.data)[1]){
  space_text <- space_tokenizer(icd.data$samenvatting[i])[[1]]
  l <- length(space_text)
  sl <- sl + l
  if(l <= 1){
    n <- n + 1
    print("----------------------------------------------")
    print(icd.data$samenvatting[i])
  }
  if(l > maxl)
    maxl <- l
  if(l < minl)
    minl <- l
}

avgl <- sl / dim(icd.data)[1]
cat("Min len after samenvatting: ", minl)
cat("Max len after samenvatting: ", maxl)
cat("AVG len after samenvatting: ", avgl)

```


## Remove empty text
```{r}
for (i in 1:dim(icd.data)[1]){
  space_text <- space_tokenizer(icd.data$deidentified[i])[[1]]
  l <- length(space_text)
  if(l <= 2){
    print(icd.data$deidentified[i])
    icd.data <- icd.data[-c(i), ]
  }
}

```



```{r}
selected_ICDs <- data.frame(icdCode = c("I25", "I10", "I48", "I50", "E78",
                                       "E11", "I42", "I21", "N18", "Z95"))
icd.data.selected <- icd.data[icd.data$Diagnosecodeerst %in% selected_ICDs$icdCode,]
length(unique(icd.data.selected$PATIENT_ID_VOORKEUR))

icd.data.selected <- icd.data.selected[ ,c("PATIENT_ID_VOORKEUR", 
                                           "deidentified",
                                           "samenvatting", 
                                           "Age.at.letter",
                                           "Geslacht", 
                                           "Diagnosecodeerst")
                                        ]

icd.data.selected <- icd.data.selected %>% 
  dplyr::rename(
    ID      = PATIENT_ID_VOORKEUR,
    text    = deidentified,
    age     = Age.at.letter,
    gender  = Geslacht,
    icdcode = Diagnosecodeerst
    )

```

## Data for multi-label
```{r}
icd.data.multilabel.selected <- icd.data.selected %>%
  group_by(ID, text) %>%
  summarize(
    text.m       = paste(text, collapse = 'THISISSPACE'),
    samenvatting = paste(samenvatting, collapse = 'THISISSPACE'),
    age          = unique(age),
    gender       = unique(gender),
    # chapter    = paste(Diagnosechapter, collapse = ','),
    icdcode      = paste(icdcode, collapse = ','),
    # fullcode   = paste(Diagnosecode, collapse = ','),
    )

# icd.data.multilabel.selected$chapter <- 
#   sapply(strsplit(icd.data.multilabel.selected$chapter, ","), 
#          function(x) paste(unique(x), collapse = ","))

icd.data.multilabel.selected$icdcode <- 
  sapply(strsplit(icd.data.multilabel.selected$icdcode, ","), 
         function(x) paste(unique(x), collapse = ","))

# icd.data.multilabel.selected$fullcode <- 
#   sapply(strsplit(icd.data.multilabel.selected$fullcode, ","), 
#          function(x) paste(unique(x), collapse = ","))

icd.data.multilabel.selected$text <- 
  sapply(strsplit(icd.data.multilabel.selected$text.m, "THISISSPACE"), 
         function(x) paste(unique(x), collapse = ","))
icd.data.multilabel.selected[c("text.m")] <- list(NULL)

icd.data.multilabel.selected$samenvatting <- 
  sapply(strsplit(icd.data.multilabel.selected$samenvatting, "THISISSPACE"), 
         function(x) paste(unique(x), collapse = ","))

```


## Write in csv and excel
```{r}
# write in excel for Python
path = "Data/"
# write.xlsx(icd.data1, 
#            paste(path, "icd_data_singlelabel.xlsx", sep = ""))
# write.xlsx(data.frame(icd.data.multilabel.selected), 
#            paste(path, "icd_data_multilabel.xlsx" , sep = ""))

# write in csv for Python
write_csv(icd.data.selected, 
          paste(path, "icd_selected_data_singlelabel.csv", sep = ""))
write.csv(icd.data.multilabel.selected, 
          paste(path, "icd_selected_data_multilabel.csv" , sep = ""))

```



```{r}
# for OTHER icds
`%notin%` <- Negate(`%in%`)
icd.data2 <- icd.data[icd.data$Diagnosecodeerst %notin% selected_ICDs$icdCode,]
icd.data2 <- icd.data    %>%
     group_by(PATIENT_ID_VOORKEUR, deidentified) %>%
     summarize(
       text             = paste(deidentified, collapse = 'THISISSPACE'),
       chapter          = paste(Diagnosechapter, collapse = ','),
       rolledup         = paste('Other'),
       fullcode         = paste(Diagnosecode, collapse = ','),
       samenvatting     = paste(samenvatting, collapse = 'THISISSPACE'),
       )

unique_Other  <- 
  icd.data.multilabel.selected[icd.data.multilabel.selected$rolledup == "Other",]

icd.data.multilable.withother <- 
  rbind(icd.data.multilabel.selected, unique_Other)

# `%notin%` <- Negate(`%in%`)
# icd.data[icd.data$Diagnosecodeerst %notin% selected_ICDs$icdCode,]$Diagnosecodeerst <- "Other"

```



```{r}
# icd.data.multilabel.selected$text <- clean_text(icd.data.multilabel.selected$text)

udf <- unlist(strsplit(icd.data.multilabel.selected$text, "[^[:alnum:]]"))

table(udf)
totalTokens  <- length(udf)
# Nb of unique tokens
uniqueTokens <- length(table(udf))
# Avg nb of tokens / records
totalTokens / dim(icd.data.multilabel)[1]

## counting labels again
ldf <- unlist(strsplit(icd.data.multilabel$fullcode, ","))
table(ldf)
totallabels <- length(ldf)
uniquelabels <- length(table(ldf))
totallabels / dim(icd.data.multilabel)[1]

# %labels with 50+ records
df_code <- icd.data %>%
  group_by(Diagnosecode) %>%
  summarise(counts = n())

View(df_code)
df_code_sub <- subset(df_code, counts > 49)
View(df_code_sub)

dim(df_code_sub)[1] / dim(df_code)[1]

# remove the lines with icd10 occuring less than 50 times
DiagnosecodeMorethan50 <- df_code_sub$Diagnosecode
# apply the line for icd.data.multilabel---> run prev chunk again

icd.data1 <- icd.data1[icd.data1$Diagnosecode %in% DiagnosecodeMorethan50,]

```

## MAGGIC Clusters
```{r}
# class1: E10, E11, E13 (Diabetes)
# class2: I25, I42, I43, I50 (HF)
# class3: J44 (COPD)
icd.data$Diagnoseclass <- gsub("E10", "Diabetes", icd.data$Diagnosecodeerst)
icd.data$Diagnoseclass <- gsub("E11", "Diabetes", icd.data$Diagnoseclass)
icd.data$Diagnoseclass <- gsub("E13", "Diabetes", icd.data$Diagnoseclass)

icd.data$Diagnoseclass <- gsub("I25", "HF", icd.data$Diagnoseclass)
icd.data$Diagnoseclass <- gsub("I42", "HF", icd.data$Diagnoseclass)
icd.data$Diagnoseclass <- gsub("I43", "HF", icd.data$Diagnoseclass)
icd.data$Diagnoseclass <- gsub("I50", "HF", icd.data$Diagnoseclass)

icd.data$Diagnoseclass <- gsub("J44", "COPD", icd.data$Diagnoseclass)

table(icd.data$Diagnoseclass)

```


## Text analysis
```{r}
frequent_terms <- freq_terms(icd.data$deidentified, 30)

ggplot(frequent_terms, 
       aes(x = reorder(WORD, FREQ), y = FREQ)) + 
  geom_bar(stat = "identity")          + 
  coord_flip()                         + 
  xlab("Word in patient letters")      + 
  ylab("Count")                        +
  theme_minimal()

wordcloud(icd.data$deidentified, min.freq = 10, random.order = FALSE, 
          colors = brewer.pal(8, "Dark2"))

```


## Splitting the text based on the sections: ... (Arjan)
```{r}
# data.p2 <- data
# data.p2$text <- substring(data.p2$text, 
#                           regexpr("thorax", data.p2$text) + 7)

```


## Preprocessing 2
```{r}
clean_text  <- function(text){
  text      <- tolower(text)
  # removePunctuation(text) is replaced by the following line
  # need space replacing punctuations
  text      <- gsub("[[:punct:][:blank:]]+", " ", text)   
  text      <- stripWhitespace(text)
  text      <- removeNumbers(text)
  # new_stops <- read.table("stop.txt", header = TRUE)
  # new_stops <- as.vector(new_stops$CUSTOM_STOP_WORDS)
  # text      <- removeWords(text, new_stops)
  return(text)
}

# add as many words as you want into the stop.txt file

```

## Cleaning:
```{r}
icd.data$deidentified <- clean_text(icd.data$deidentified)
frequent_terms_p      <- freq_terms(icd.data$deidentified, 50)

```

## Most frequent terms after calling clean_text function:
```{r}
frequent_terms_p %>% ggplot(aes(x = reorder(WORD, FREQ), y = FREQ)) + 
  geom_bar(stat = "identity")          + 
  coord_flip()                         + 
  xlab("Word in patient letters")      + 
  ylab("Count")                        +
  theme_minimal()

```


## Stemming
```{r}
icd.data$deidentified <- stemDocument(icd.data$deidentified, 
                                      language = "dutch")
frequent_terms_s <- freq_terms(icd.data$deidentified, 30)

```

## Most frequent terms after applying stemming:
```{r}
ggplot(frequent_terms_s, aes(x = reorder(WORD, FREQ), y = FREQ)) + 
  geom_bar(stat = "identity")          + 
  coord_flip()                         + 
  xlab("Word in patient letters")      + 
  ylab("Count")                        +
  theme_minimal()

```


## Removing empty text
```{r}
for (i in 1:dim(icd.data)[1]){
  space_text <- space_tokenizer(icd.data$deidentified[i])[[1]]
  if(length(space_text) <= 2){
    print(icd.data$deidentified[i])
    icd.data <- icd.data[-c(i), ]
  }
}

```


## Training and test sets
```{r}
set.seed(321)

data_part  <- createDataPartition(y = icd.data$Diagnoseclass, 
                                  p = 0.8, list = F)
test.data  <- icd.data[-data_part,] # 20% data goes here
train.data <- icd.data[data_part,] # 80% here

X <- train.data$deidentified
Y <- train.data$Diagnoseclass

```


## Training set
```{r}
vc  <- VCorpus(VectorSource(X)) # VCorpus(VectorSource(icd.data$deidentified))
dtm <- DocumentTermMatrix(vc)
# inspect(dtm)

```

## Test set
```{r}
vc  <- VCorpus(VectorSource(test.data$deidentified))
dtm.test <- DocumentTermMatrix(vc)

```


# icd ~ bag_of_words

## Train LR
```{r}
set.seed(321)
# X_training_BOW <- as.matrix(dtm)

bow.cv.fit <- cv.glmnet(data.matrix(dtm), 
              data.matrix(Y),
              family           = "multinomial",
              type.multinomial = "grouped", 
              nfolds           = 5)

bow.pred <- predict(bow.cv.fit, 
                    newx = data.matrix(dtm), 
                    type = 'class',
                    s    = "lambda.min")

lrtab <- table(Y, bow.pred)
lrtab


```

```{r}
n = sum(lrtab) # number of instances
nc = nrow(lrtab) # number of classes
diag = diag(lrtab) # number of correctly classified instances per class 
rowsums = apply(lrtab, 1, sum) # number of instances per class
colsums = apply(lrtab, 2, sum) # number of predictions per class
p = rowsums / n # distribution of instances over the actual classes
q = colsums / n # distribution of instances over the predicted classes
accuracy = sum(diag) / n
cat("Accuracy for LR is: ", accuracy)
precision = diag / colsums
cat("\nPrecision for LR is: ", precision)
recall = diag / rowsums
cat("\nRecall for LR is: ", recall)
f1 = 2 * precision * recall / (precision + recall) 
cat("\nf1-score for LR is: ", f1)

macroPrecision = mean(precision)
macroRecall = mean(recall)
macroF1 = mean(f1)

data.frame(precision, recall, f1)
data.frame(macroPrecision, macroRecall, macroF1)
avgAccuracy = sum(diag(lrtab)) / sum(lrtab)
avgAccuracy

```


## SVM e1071
```{r}
set.seed(321)    # Set seed for reproducible results
svm1 <- svm(x      = data.matrix(X_training_BOW[, -1]), 
            y      = X_training_BOW[, 1],
            type   = "C-classification",
            kernel = "linear",
            probability = TRUE)

summary(svm1)
svm1$SV

prediction <- predict(svm1, data.matrix(dtm.test))
svmtab <- table(test.data$Diagnoseclass, prediction)
svmtab

```


## Train SVM
```{r}
TrainCtrl <- trainControl(method  = "repeatedcv", 
                          number  = 5, 
                          repeats = 3,
                          classProbs = TRUE,
                          verbose = FALSE)

set.seed(321) 
# SVMgrid <- expand.grid(sigma = c(0.05, 0.0456, 0.0577), 
# C = c(1.5, 1.596, 1.65, 1.89, 1.95, 2, 2.2, 2.44))
# SVMgrid <- expand.grid(sigma = c(0.0577), C = c(2.21049))
Svm_model <- train(data.matrix(dtm),
                     Y, 
                     method     = "svmLinear", 
                     trControl  = TrainCtrl, 
                     # tuneGrid = SVMgrid, 
                     verbose = FALSE)


PredictedTest <- predict(Svm_model, data.matrix(dtm.test))

Accuracy(PredictedTest, test.data$Diagnoseclass)

```


## TFiDF matrix
```{r}
create_tfidf_matrix <- function(dtm){
  # construct the matrix of term counts to get the IDF vector
  tf_mat <- TermDocFreq(dtm)
  # TF-IDF and cosine similarity
  tfidf  <- t(dtm[ , tf_mat$term]) * tf_mat$idf
  tfidf  <- t(tfidf)
  return(tfidf)
}

```


## LSTM
```{r}
maxlen <- 80 # length of each document
y_binary = to_categorical(as.numeric(icd.data$Diagnoseclass)) # one-hot encoding
cat('Pad sequences (samples x time)\n')
xb_train <- pad_sequences(X_bag_of_words, maxlen = maxlen)
cat('x_train shape:', dim(xb_train), '\n')

max_features = dim(dtm)[2]

cat('Build model...\n')
model <- keras_model_sequential()

model                                                %>%
  layer_embedding(input_dim  = max_features, 
                  output_dim = 100)                  %>% 
  bidirectional(layer_lstm(units   = 100, 
                           dropout = 0.2, 
                           recurrent_dropout = 0.2)) %>%
  layer_flatten()                                    %>% 
  layer_dense(units      = 22, 
              activation = 'softmax')

# Try using different optimizers and different optimizer configs
model %>% compile(
  loss      = 'categorical_crossentropy',
  optimizer = 'adam',
  metrics   = c('accuracy')
)

```

```{r}
cat('Train...\n')
model %>% fit(
  x          = xb_train, 
  y          = y_binary,
  batch_size = 64,
  epochs     = 50,
  # validation_data = list(x_test = xb_train, y_test = tr_classes)
)

scores <- model %>% evaluate(xb_train, y_binary)
cat('Test score:', scores[[1]])
cat('Test accuracy', scores[[2]])

prediction <- model %>% predict_classes(xb_train)
# levels(tr_classes)
t <- table(true = as.numeric(icd.data$Diagnoseclass), pred = prediction)

```

